\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel-space

### 2012-04-29 evaluation.tex
update eval

\begin{figure*}[t!]
	\begin{center}
	\begin{tabular}{|l||c|c|c|c||c|}
		\hline
		\multirow{2}{*}{\bf Kernel and test case} & \multicolumn{4}{c||}{\bf Custom decision points} & \multirow{2}{*}{\bf Stress test} \\
		\cline{2-5}
		& \bf default & \bf lock & \bf unlock & \bf both & \\
		\hline\hline
		POBBLES vanish/vanish (a) & \nobugnum{31.8}{0.6} & \bugnum{57.1}{1.7} & $\infty$ & $\infty$ & \\
		\hline
		POBBLES vanish/vanish (b) & \nobugnum{32}{0.4} & \bugnum{51.5}{2.1} & & $\infty$ & \\
		\hline
		POBBLES wait/wait & \bugnum{23.3}{0.7} & \bugnum{27.9}{0.8} & \bugnum{27.9}{2.1} & \bugnum{41.6}{1.4} & \\
		\hline
		POBBLES thread\_fork/vanish & \bugnum{22}{0.6} & \bugnum{37.4}{1.1} & \bugnum{27.6}{0.5} & \bugnum{72}{2.6} & \\
		\hline
		LudicrOS vanish/vanish & \nobugnum{13.2}{0.2} & \bugnum{13.7}{0.7} & \bugnum{34.6}{1.1} & \bugnum{17.1}{0.3} & \\
		\hline
		LudicrOS yield/vanish & \nobugnum{12.3}{0.3} & \bugnum{11.4}{0.4} & \nobugnum{27.4}{0.8} & \bugnum{11.7}{0.4} & \\
		\hline
	\end{tabular}
	\end{center}
	\caption{Comparison of time taken (in seconds) to find bugs using Landslide and using conventional stress testing.
	Landslide's times are given for several different sets of decision points: the default set, consisting only of voluntary reschedules (Section~\ref{sec:components-arbiter}); and using custom decision points in addition to the default set: calls to \texttt{mutex\_lock}, calls to \texttt{mutex\_unlock}, and both.
	All numbers represent the average elapsed time in seconds from 5 trials, and the standard deviation is shown in parentheses. ``\nobugnum{$X$}{$s$}'' indicates the bug was not found with a given test setup (and instead, Landslide took $X$ time to explore the entire decision tree). ``$\infty$'' indicates the bug was not found with stress testing (after 1 hour), or that Landslide's search did not finish (after 8 hours). % TODO: after how long? what timeout?
	}
	\label{fig:numbers}
\end{figure*}

@@

\newcommand\bugtree[1]{\textcolor{BrickRed}{\bf #1}}
\newcommand\nobugtree[1]{\textcolor{Blue}{\em #1}}
\begin{figure*}[t!]
	\begin{center}
	\begin{tabular}{|l|l||c|c|c|c|}
		\hline
		\multirow{2}{*}{\bf Kernel and test case} & \multirow{2}{*}{\bf Property of tree} & \multicolumn{4}{|c|}{\bf Custom decision points} \\
		\cline{3-6}
		& & \bf default & \bf lock & \bf unlock & \bf both \\
		\hline\hline
		\multirow{4}{*}{POBBLES vanish/vanish (a)} & Decision points & \nobugtree{56} & \bugtree{1296} & N/A & N/A \\
		& Total backtracks   & \nobugtree{16} & \bugtree{376} & N/A & N/A \\
		& Average branch depth & \nobugtree{5} & \bugtree{19} & N/A & N/A \\
		\hline
		\multirow{4}{*}{POBBLES vanish/vanish (b)} & Decision points & \nobugtree{56} & \bugtree{1295} & \nobugtree{382071} & N/A \\
		& Total backtracks   & \nobugtree{16} & \bugtree{376} & \nobugtree{112706} & N/A \\
		& Average branch depth & \nobugtree{5} & \bugtree{17} & \nobugtree{16} & N/A \\
		\hline
		\multirow{4}{*}{POBBLES wait/wait} & Decision points & \bugtree{23} & \bugtree{102} & \bugtree{74} & \bugtree{378} \\
		& Total backtracks   & \bugtree{4} & \bugtree{17} & \bugtree{12} & \bugtree{56} \\
		& Average branch depth & \bugtree{6} & \bugtree{10} & \bugtree{9} & \bugtree{14} \\
		\hline
		\multirow{4}{*}{POBBLES thread\_fork/vanish} & Decision points & \bugtree{24} & \bugtree{394} & \bugtree{273} & \bugtree{2269} \\
		& Total backtracks   & \bugtree{5} & \bugtree{70} & \bugtree{56} & \bugtree{410} \\
		& Average branch depth & \bugtree{5} & \bugtree{16} & \bugtree{14} & \bugtree{23} \\
		\hline
		\multirow{4}{*}{LudicrOS vanish/vanish} & Decision points & \nobugtree{10} & \bugtree{16} & \bugtree{141} & \bugtree{42} \\
		& Total backtracks   & \nobugtree{2} & \bugtree{3} & \bugtree{48} & \bugtree{10} \\
		& Average branch depth & \nobugtree{2} & \bugtree{7} & \bugtree{9} & \bugtree{14} \\
		\hline
		\multirow{4}{*}{LudicrOS yield/vanish} & Decision points & \nobugtree{8} & \bugtree{5} & \nobugtree{149} & \bugtree{7} \\
		& Total backtracks   & \nobugtree{1} & \bugtree{0} & \nobugtree{43} & \bugtree{0} \\
		& Average branch depth & \nobugtree{2} & \bugtree{0} & \nobugtree{9} & \bugtree{0} \\
		\hline
	\end{tabular}
	\end{center}
	\caption{Information about the decision trees explored when finding bugs. As in the previous table, each test case was run with the four different sets of decision points. ``\nobugtree{X}'' means the tree was completely explored because Landslide did not find a bug in that configuration. ``\bugtree{X}'' reflects the portion of the tree that was explored before a bug was found.}
	\label{fig:trees}
\end{figure*}

@@

\subsubsection{Recommended Testing Strategies}

>>>>

\begin{figure*}[t!]
	\begin{center}
	\begin{tabular}{|l||c|c|c|c||c|}
		\hline
		\multirow{2}{*}{\bf Kernel and test case} & \multicolumn{4}{c||}{\bf Decision points used} & \multirow{2}{*}{\bf Stress test} \\
		\cline{2-5}
		& \bf default & \bf lock & \bf unlock & \bf both & \\
		\hline\hline
		POBBLES vanish/vanish (a) & \nobugnum{31.8}{0.6} & \bugnum{57.1}{1.7} & $\infty$ & $\infty$ & \\
		\hline
		POBBLES vanish/vanish (b) & \nobugnum{32}{0.4} & \bugnum{51.5}{2.1} & \nobugnum{8057.9}{336.9} & $\infty$ & \\
		\hline
		POBBLES wait/wait & \bugnum{23.3}{0.7} & \bugnum{27.9}{0.8} & \bugnum{27.9}{2.1} & \bugnum{41.6}{1.4} & \\
		\hline
		POBBLES thread\_fork/vanish & \bugnum{22}{0.6} & \bugnum{37.4}{1.1} & \bugnum{27.6}{0.5} & \bugnum{72}{2.6} & \\
		\hline
		LudicrOS vanish/vanish & \nobugnum{13.2}{0.2} & \bugnum{13.7}{0.7} & \bugnum{34.6}{1.1} & \bugnum{17.1}{0.3} & \\
		\hline
		LudicrOS yield/vanish & \nobugnum{12.3}{0.3} & \bugnum{11.4}{0.4} & \nobugnum{27.4}{0.8} & \bugnum{11.7}{0.4} & \\
		\hline
	\end{tabular}
	\end{center}
	\caption{Comparison of time taken (in seconds) to find bugs using Landslide and using conventional stress testing.
	Landslide's times are given for several different sets of decision points: the default set, consisting only of voluntary reschedules (Section~\ref{sec:components-arbiter}); and using custom decision points in addition to the default set: calls to \texttt{mutex\_lock}, calls to \texttt{mutex\_unlock}, and both.
	All numbers represent the average from 5 trials, with the standard deviation shown in parentheses. ``\nobugnum{$X$}{$s$}'' indicates the bug was not found with a given test setup (and instead, Landslide took $X$ time to explore the entire decision tree). ``$\infty$'' indicates the bug was not found with stress testing (after 1 hour), or that Landslide's search did not finish (after 8 hours). % TODO: after how long? what timeout?
	}
	\label{fig:numbers}
\end{figure*}

@@

\newcommand\bugtree[1]{\textcolor{BrickRed}{\bf #1}}
\newcommand\nobugtree[1]{\textcolor{Blue}{\em #1}}
\begin{figure*}[t!]
	\begin{center}
	\begin{tabular}{|l|l||c|c|c|c|}
		\hline
		\multirow{2}{*}{\bf Kernel and test case} & \multirow{2}{*}{\bf Property of tree} & \multicolumn{4}{|c|}{\bf Decision points used} \\
		\cline{3-6}
		& & \bf default & \bf lock & \bf unlock & \bf both \\
		\hline\hline
		\multirow{4}{*}{POBBLES vanish/vanish (a)} & Decision points & \nobugtree{56} & \bugtree{1296} & N/A & N/A \\
		& Total backtracks   & \nobugtree{16} & \bugtree{376} & N/A & N/A \\
		& Average branch depth & \nobugtree{5} & \bugtree{19} & N/A & N/A \\
		\hline
		\multirow{4}{*}{POBBLES vanish/vanish (b)} & Decision points & \nobugtree{56} & \bugtree{1295} & \nobugtree{382071} & N/A \\
		& Total backtracks   & \nobugtree{16} & \bugtree{376} & \nobugtree{112706} & N/A \\
		& Average branch depth & \nobugtree{5} & \bugtree{17} & \nobugtree{16} & N/A \\
		\hline
		\multirow{4}{*}{POBBLES wait/wait} & Decision points & \bugtree{23} & \bugtree{102} & \bugtree{74} & \bugtree{378} \\
		& Total backtracks   & \bugtree{4} & \bugtree{17} & \bugtree{12} & \bugtree{56} \\
		& Average branch depth & \bugtree{6} & \bugtree{10} & \bugtree{9} & \bugtree{14} \\
		\hline
		\multirow{4}{*}{POBBLES thread\_fork/vanish} & Decision points & \bugtree{24} & \bugtree{394} & \bugtree{273} & \bugtree{2269} \\
		& Total backtracks   & \bugtree{5} & \bugtree{70} & \bugtree{56} & \bugtree{410} \\
		& Average branch depth & \bugtree{5} & \bugtree{16} & \bugtree{14} & \bugtree{23} \\
		\hline
		\multirow{4}{*}{LudicrOS vanish/vanish} & Decision points & \nobugtree{10} & \bugtree{16} & \bugtree{141} & \bugtree{42} \\
		& Total backtracks   & \nobugtree{2} & \bugtree{3} & \bugtree{48} & \bugtree{10} \\
		& Average branch depth & \nobugtree{2} & \bugtree{7} & \bugtree{9} & \bugtree{14} \\
		\hline
		\multirow{4}{*}{LudicrOS yield/vanish} & Decision points & \nobugtree{8} & \bugtree{5} & \nobugtree{149} & \bugtree{7} \\
		& Total backtracks   & \nobugtree{1} & \bugtree{0} & \nobugtree{43} & \bugtree{0} \\
		& Average branch depth & \nobugtree{2} & \bugtree{0} & \nobugtree{9} & \bugtree{0} \\
		\hline
	\end{tabular}
	\end{center}
	\caption{Information about the decision trees explored when finding bugs. As in the previous table, each test case was run with the four different sets of decision points. ``\nobugtree{X}'' means the tree was completely explored because Landslide did not find a bug in that configuration. ``\bugtree{X}'' reflects the portion of the tree that was explored before a bug was found.}
	\label{fig:trees}
\end{figure*}

@@

\subsubsection{Recommended Testing Strategies}
\label{sec:discussion-strategies}
